### 2013-12-03 msc-thesis/chapters/1/chapter-intro.tex
MSC Added in 2 motivational studies.

The main goal of this document was to set up competently the Latex framework for a thesis document at UVic, with all the assorted details of front pages, numbering and so on. In order to present such a template to other users, the content has been filled from the guidelines of an experienced graduate advisor and supervisor on how to write a thesis in the first place.

The Latex framework given in these files should work in the Windows, Mac and Unix environments. In Windows, the development environment is MikTex, available as a free download from the web page at \textit{miktex.org}. Miktex includes all the tools for \LaTeX, without a convenient editor. I have been using
\textit{WinEdt} which is still the best as far as working in a well integrated manner with MikTex, even if one has to pay a small price. \textit{WinEdt} is available from \textit{winedt.com}. The corresponding package for the Mac is MacTex, available from \textit{www.tug.org$\backslash$mactex}.
Please note that in the actual file with the \LaTeX code there are extra local comments referring to small differences between platforms. This is especially crucial for the insertion of figures of any type (see also Chapter 3).

The package \textit{BibTex} is used for the automatic bibliography and it is incorporated in the MikTex package. The style of bibliography exemplified is this document is the "plain" one,
most often used in science theses. This is shown
by the entry \textit{plain} in the \textit{bibliographystyle}
command which can be found in the top file, namely
\textit{mainthesisUVIC.tex}. Substitute the
appropriate bibliography style for your needs by finding
the correct parameter. In order to help you there is a PDF
file entitled: "InformationOnBibliographyStyles.pdf" in the
same folder as the top file \textit{mainthesisUVIC.tex}.

The title pages are correctly formatted according to the guidelines. However the superset is given here as a template for a Ph.D. dissertation and adjustments must be made for a Master's thesis accordingly.

When presented with the task of having to write a large document reporting on the work done for the thesis portion of a graduate degree most people have anxiety attacks. It seems that the research work has been done, probably with great competence, yet one feels totally lost on how to approach the writing part - unless of course one is a writer to start with. While I am not at all the expert, I have experience both in writing documents and in supervising many graduate students. I have developed a simple enough structure which guides me and my students most of the times fairly well. We then customize it for different audiences and situations. The content of this pseudo mini thesis summarizes the structure I use.

This document, however, is \textit{not at all} a Latex manual. There are a few examples sprinkled here and there of various commands. However no explanations or full examples are given for how to use Latex itself. That is most certainly left to the user!

Starting at the very beginning, my first step is to set up the formatting framework before the content itself, just like the frame of a building is the sustaining structure. By having the content only in bullet points which can be moved and changed at will I can have a whole document which will always compile and be ready for presentation. I ask my student to prepare mock chapters which contains only these bulleted lists to be used for discussion. The bulleted list I had for this chapter is as follows:
\begin{enumerate}
        \item State the dual purpose of this document (just mention briefly);
        \item State what this document is not (just mention);
        \item Describe what I think should go in the Introduction in general;
        \item Describe what I think should not go in the "Introduction" chapter in general;
        \item Describe the structure of the document.
\end{enumerate}

When the writing for a chapter is particularly long, it might be better to have some, if not all, sections in separate files. It makes it a lot easier to find possible errors in Latex as well, since the command to input a file for a separate section can always be commented out. When looking at the \textit{.tex} file itself for this introduction chapter you will notice that there are 2 sections, namely "How to Start an Introduction" and "Is a Review of All previous Work Necessary Here?" which are included as separate files, immediately following this paragraph.
\input chapters/1/sec-intro
\input chapters/1/sec-review
%\pagebreak
\section{My Claims}
Something must be new in this work, no matter how small, since you are getting a graduate degree for it! Tell me about it clearly and succintly right now, just as you did in the abstract. Make an impact here. How about something like the following box:

I make \textit{four} claims which
my dissertation validates:
\\

\framebox{%
\parbox{5in}{
	My new algorithm to solve the problem of doing nothing include these important new features whose practical applicability can be proved both formally and empirically:
	\begin{enumerate}
	\item first feature;
	\item second feature;
	\item everything is much easier to understand, and therefore, easier to implement correctly.
	\end{enumerate}
}}
\\

\noindent Claim 1 and claim 2 are \textit{quantitative} - they will be proven by experiment.

\noindent Claim 3 is \textit{qualitative} - they will be demonstrated by argument.

\subsection{The Importance of My Claims}

Some very important positive consequences
arise from the validation of the above claims.
It is these consequences that comprise a significant
positive contribution to research in the field
of whatever the field is.
\\

\noindent Claim 1 implies that:
\begin{enumerate}
\item{Something profound which applies to:
	\begin{itemize}
	\item {something excellent;}
	\item {something important.}
	\end{itemize}}
\item{Something else just as profound.}
\end{enumerate}

\noindent Claim 2 implies that:
\begin{itemize}
\item{Repeat as above if necessary and useful.}
\end{itemize}

\noindent The consequence of claim 3 is that:
\begin{itemize}
\item{There must be something good coming out of all this work!}
\end{itemize}

\section{Agenda}

This section provides a map of the dissertation
to show the reader where and how it validates
the claims previously made. Here is where I am also presenting my own style of organization which may be totally different from what your supervisor thinks. However, trust me, this is a good solid beginning for a structure. Your supervisor may ask you to change it, but will still appreciate what you have! For each of the chapters below I also give a short summary of what the main focus should be and then I expand on it  a bit within the chapter itself.

\begin{description}
\item[\textbf{Chapter 1}] contains a statement of
the claims which will be proved by this dissertation followed by an overview of the structure of the document itself.
\item[\textbf{Chapter 2}] describes in details the open problem which is to be tackled together with its context, its impact and the overall motivation for the research overall.
\item[\textbf{Chapter 3}] gives the new research, its methodology, the algorithms involved, the new solution, the new work done. Formal proofs and arguments are made here. This is the first of the two contributions expected in a thesis for a graduate degree.
\item[\textbf{Chapter 4}] is where the experiments and the methodology for them is fully described. The first part includes all details of how the empirical side of the research has been conducted. Note that not every thesis has this empirical portion.
\item[\textbf{Chapter 5}] includes the evaluation of the data presented above and the comparisons with the work of others, to show how much better the new approach is. This is the second of the two contributions expected in a thesis for a graduate degree. Note that this part could be consolidated into the chapter above.
\item[\textbf{Chapter 6}] contains a restatement of the claims and results of the dissertation. It also enumerates avenues of future work for further development of the concept and its applications.
\end{description}

The list above is not complete. Chapter 3 actually includes a lot more, as I could not resist placing in it a few \LaTeX examples to help you along. This document is not a primer for \LaTeX, but there is no harm done in giving a little help.

>>>>

\input chapters/1/sec-intro
\input chapters/1/sec-review

### 2013-12-03 msc-thesis/chapters/2/sec-developer-pairs.tex
MSC Added in 2 motivational studies.

% This will be the main document for the Technical Networks paper to
% be written by the Eggnet team of Jordan Ell, Triet Huynh and Braden
% Simpson in association with Adrian Schroeter and Daniela Damian.

\documentclass[conference]{IEEEtran}

% Use of outside images
\usepackage{graphicx} 
% Use text inside euqations
\usepackage{amsmath}

\usepackage{balance}
\usepackage{float}
\floatstyle{plaintop}
\restylefloat{table}

% Correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

% Begin the paper here
\begin{document}

% Paper title
% Can use linebreaks \\ within to get better formatting as desired
\title{Identifying Failure Inducing Developer Pairs within Developer Networks}

% Authors names
\author{\IEEEauthorblockN{Jordan Ell}
\IEEEauthorblockA{University of Victoria,
Victoria, British Columbia, Canada \\ jell@uvic.ca}
}

% Make the title area
\maketitle

\begin{abstract}
Software systems have not only become larger over time, but the amount of
technical contributors and dependencies have also increased. With these expansions also comes
the increasing risk of introducing a software failure into a pre-existing system.
Software failures are a multi-billion dollar problem in the industry today and while integration and
other forms of testing are helping to ensure a minimal number of failures, research to understand
full impacts of code changes and their social implications is still a major concern. This paper describes
how analysis of code changes and the technical relationships they infer can be used to detect pairs
of developers whose technical dependencies may induce software failures. These developer pairs may
also be used to predict future software failures as well as provide recommendations to contributors
to solve these failures caused by source code changes.
\end{abstract}

\section{Introduction}

% Setup the problem.
Large software projects are created using highly modular and 
reusable code. This creates technical dependencies between methods or functions
that can be used in a wide variety of locations throughout the project. 
This causes changes to any given method to have a rippling 
effect across the rest of the project~\cite{Acharya:2011:PCI}. The larger these effects are,
the more likely they are to cause a software failure inside the system during the project's
life span~\cite{Zimmermann:2008:PDU}. These observations of technical dependencies open
the door to types of analysis on the developer networks they infer and preventing software
failures by improving coordination amongst dependant developers.

@@

% Research question
With the power of technical dependencies in predicting software failures, the question I
investigated in this project is : 
``\textit{Is it possible to identify pairs of developers whose technical dependencies in code changes
statistically relate to bugs?}''

% Explain our brief intended approach
This paper explains the approach used to locate these pairs of developers in developer networks.
The process utilizes code changes and the call hierarchies effected  to find patterns of developer 
relationships in successful and failed code changes.  These developer relationships can also be used
to promote the idea of leveraging socio-technical congruence, a measure of coordination compared
to technical dependencies amongst stakeholders, to provide coordination recommendations.

% Technical network figure
\begin{figure*}[tb!]
\centering
\includegraphics[width=0.9\textwidth]{images/TecNetwork}
\caption{A technical network for a code change. Carl has changed method getX() which is being
called by Bret's method foo() as well as Daniel and Anne's method bar().\label{fig:network}}
\end{figure*}

\section{Technical Approach}

\subsection{Extracting Technical Networks}
% End goal
The basis of this approach is to create a technical network of developers based on method ownership
and those methods' call hierarchies effected by code changes. These networks will provide
dependency edges between contributors caused by code changes which may be 
identified as possible failure inducing pairings (Figure~\ref{fig:network}). To achieve this goal,
developer owners of methods, method call hierarchies (technical
dependencies) and code change effects on these hierarchies must be identified.
This approach is described in detail by illustrating its application to mining the data in a Git
repository although it can be used with any software repository.

@@

\subsection{Identifying Failure Inducing Developer Pairs}
To identify failure inducing developer pairs (edges) inside technical networks, 
edges in relation to discovered code change failures are now analysed. To determine whether a code change 
was a success or failure (introduce a software failure), the approach of
Sliwerski et al.~\cite{Sliwerski:2005:CIF} is used. The following steps are then taken:

@@

\section{Results}
To illustrate the use of the approach, I conducted a case study of
the Hibernate-ORM project, an open source Java 
application hosted on GitHub\footnote{https://github.com/} with issue tracking 
performed by Jira\footnote{http://www.atlassian.com/software/jira/overview}.

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{@{\hspace{.2cm}}ccc@{\hspace{.75cm}}c@{\hspace{.2cm}}c@{\hspace{.2cm}}}
\hline
Pair & Successful & Failed & FI & P-Value\\
\hline
(Daniel, Anne)	&	0&	14&	1.0000& 0.0001249		\\
(Carl, Bret)	&	1&	12&	0.9190& 0.003468	\\
(Emily, Frank)	&	1&	9&	0.8948& 0.02165      \\
\hline
\end{tabular}
\end{center}
\caption{Top 3 failure inducing developer pairs found.\label{tab:ratio}}
\end{table}

\section{Conclusion and Future Work}
Technical dependencies are often used to predict software failures
in large software system~\cite{Pinzger:2008:DNP, Zimmermann:2008:PDU, Kim:2006:AIB}. 
This paper has presented a method for detecting failure inducing pairs of developers inside
of technical networks based on code changes. These developer pairs can be used in the prediction
of future bugs as well as provide coordination recommendations for developers within a project.

In future work, the adding of communication networks on a per code change basis is planned. In this,
the investigation of social and technical congruence on these networks and its effects on
software quality will be studied.

\bibliographystyle{IEEEtran}
\balance
\bibliography{paper}

% End of the paper
\end{document}

>>>>

\section{Study 1: Failure Inducing Developer Pairs}

@@

% Research question
With the power of technical dependencies in predicting software failures, the question I
investigated in this study was : 
``\textit{Is it possible to identify pairs of developers whose technical dependencies in code changes
statistically relate to bugs?}''

% Explain our brief intended approach
This study explains the approach used to locate these pairs of developers in developer networks.
The process utilizes code changes and the call hierarchies effected  to find patterns of developer 
relationships in successful and failed code changes. As it will be seen, we found 27 statistically
significant failure inducing developer pairs. These developer relationships can also be used
to promote the idea of leveraging socio-technical congruence, a measure of coordination compared
to technical dependencies amongst stakeholders, to provide coordination recommendations.

\subsection{Technical Approach}

\subsubsection{Extracting Technical Networks}
% End goal
The basis of this approach is to create a technical network of developers based on method ownership
and those methods' call hierarchies effected by code changes. These networks will provide
dependency edges between contributors caused by code changes which may be 
identified as possible failure inducing pairings (Figure~\ref{fig:network}). To achieve this goal,
developer owners of methods, method call hierarchies (technical
dependencies) and code change effects on these hierarchies must be identified.
This approach is described in detail by illustrating its application to mining the data in a Git
repository although it can be used with any software repository.

% Technical network figure
\begin{figure}[h]
\centering
\includegraphics[width=0.9\textwidth]{figures/TecNetwork}
\caption{A technical network for a code change. Carl has changed method getX() which is being
called by Bret's method foo() as well as Daniel and Anne's method bar().\label{fig:network}}
\end{figure}

@@

\subsubsection{Identifying Failure Inducing Developer Pairs}
To identify failure inducing developer pairs (edges) inside technical networks, 
edges in relation to discovered code change failures are now analysed. To determine whether a code change 
was a success or failure (introduce a software failure), the approach of
Sliwerski et al.~\cite{Sliwerski:2005:CIF} is used. The following steps are then taken:

@@

\subsection{Results}
To illustrate the use of the approach, I conducted a case study of
the Hibernate-ORM project, an open source Java 
application hosted on GitHub\footnote{https://github.com/} with issue tracking 
performed by Jira\footnote{http://www.atlassian.com/software/jira/overview}.

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{@{\hspace{.2cm}}ccc@{\hspace{.75cm}}c@{\hspace{.2cm}}c@{\hspace{.2cm}}}
\hline
Pair & Successful & Failed & FI & P-Value\\
\hline
(Daniel, Anne) & 0 & 14 & 1.0000 & 0.0001249 \\
(Carl, Bret)   & 1 & 12 & 0.9190 & 0.003468  \\
(Emily, Frank) & 1 &  9 & 0.8948 & 0.02165   \\
\hline
\end{tabular}
\end{center}
\caption{Top 3 failure inducing developer pairs found.\label{tab:ratio}}
\end{table}

\subsection{Analysis}
Technical dependencies are often used to predict software failures
in large software system~\cite{Pinzger:2008:DNP, Zimmermann:2008:PDU, Kim:2006:AIB}. 
This study has presented a method for detecting failure inducing pairs of developers inside
of technical networks based on code changes. These developer pairs can be used in the prediction
of future bugs as well as provide coordination recommendations for developers within a project.

This study however, did not consider the technical dependencies themselves to be the root cause of
the software failures. This study focused purely on developer ownership of software methods and
the dependencies between developers as the possible root cause of the failures. To study this root
cause futher, a study of indirect conflicts and their relationship to developer code ownership
will be conducted.
